Constant-round Blind Classical Verification of Quantum Sampling

### 2020-04-15 qpip0.tex
Rewrite parallel rep proto

@@

Inputs:
	\begin{itemize}
		\item Security parameter $1^\lambda$ for $\lambda\in\bbN$.
		\item Accuracy paramter $1^\varepsilon$ for the $\SampBQP$ instance
		\item Input $x\in\zo^n$ \Ethan{Or $\zo^*$?} for the $\SampBQP$ instance
	\end{itemize}

@@

Protocol:
\begin{enumerate}
%    \item Verifier start with description of quantum circuit $C$, input string $x$ 
	\item The verifier samples $r\xleftarrow{\$}[m]$. For $1\leq i\leq m$, if $i\ne r$ then set $c_i\leftarrow 0$, else set $c_i\leftarrow 1$.
	\item The prover and verifier runs $m$-fold parallel repetion of $\PiNaive$.
		That is, for $1\leq i\leq m$, run $(\PNaive, \VNaive(c_i))(1^\lambda, 1^\varepsilon, x)$.
	\item \label{step:multi-testing} If any of the testing round copies are rejected, the verifier outputs $(\Rej, \bot)$.
		Else it outputs the result from the Hadamard round copy.
\end{enumerate}
\end{protocol}

\begin{theorem}\label{thm:qpip0}
    Protocol~\ref{proto:QPIP0samp} is a $\QPIP_0$ protocol for $\SampBQP$ with $\negl(n)$ completeness error and $O(\eps)$ computational soundness error\hannote{definition}. 
\end{theorem}

>>>>

We now introduce our $\QPIP_0$ protocol $\PiSampZ$ for $\SampBQP$.
It is essentially a $m$-fold parallel repetition of $\PiNaive$.
However, instead of choosing whether to run test or Hadamard round randomly each round,
we run $m-1$ test rounds and only one Hadamard round.

@@

Inputs:
	\begin{itemize}
		\item Security parameter $1^\lambda$ for $\lambda\in\bbN$.
		\item Accuracy paramter $1^{1/\varepsilon}$ for the $\SampBQP$ instance
		\item Input $x\in\zo^{\poly(\lambda)}$ for the $\SampBQP$ instance
	\end{itemize}

@@

Protocol:
\begin{enumerate}
	\item The verifier generates $m$ independently copies of basis choices $\vec{h}=(h_1,\ldots,h_m)$ on inputs $1^\lambda, 1^{1/\varepsilon}, x$.
	\item The prover prepares $\rho^{\otimes m}$.
	\item The verifier generates $m$ key pairs for $\PiMeasure$, $\vec{pk}=(pk_1,\ldots,pk_m)$ and $\vec{sk}={sk_1,\ldots,sk_m}$, on inputs $1^\lambda$ and $\vec{h}$. It sends $\vec{pk}$ to the prover.
	\item The prover generates $\vec{y}=(y_1,\ldots,y_m)$ and $\sigma$ on inputs $\vec{pk}$ and $\rho^{\otimes m}$, and sends it to the verifier.
	\item The verifier samples $r\xleftarrow{\$}[m]$ which is the copy to run Hadamard round for.
		For $1\leq i\leq m$, if $i\ne r$ then set $c_i\leftarrow 0$, else set $c_i\leftarrow 1$. It sends $\vec{c}=(c_1,\ldots,c_m)$ to the prover.
	\item The prover generates $\vec{a}$ on inputs $pk, c, \sigma$ and sends it back to the verifier.
	\item \label{step:multi-testing}
		The verifier computes the outcome for each round.
		If any of the testing round copies are rejected, the verifier outputs $(\Rej, \bot)$.
		Else, it outputs the result from the Hadamard round copy.
\end{enumerate}
\end{protocol}

\begin{theorem}\label{thm:qpip0}
	$\PiSampZ$ is a $\QPIP_0$ protocol for $\SampBQP$ with $\negl(n)$ completeness error and computational soundness. 
	\Ethan{Its proof currently only shows $O(\varepsilon)$ accuracy.}
\end{theorem}
